\documentclass[a4paper,10pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[utf8]{inputenc}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{xcolor}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{0.75in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

% Set footskip to avoid warning
\setlength{\footskip}{10pt} % Adjust this value as needed

\urlstyle{same}

% Define custom colors
\definecolor{gray}{gray}{0.5}

% Adjust title format
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{gray}\titlerule\vspace{-5pt}]

% Custom command for section titles with explicit margin
\newcommand{\SectionTitle}[1]{\vspace{0.2cm}\noindent\textbf{#1}\\}

\begin{document}

% Contact Information
\begin{center}
  {\huge \scshape PAUL JOSE} \\ \vspace{1pt}
  \small 
  \href{mailto:pauljose513@gmail.com}{pauljose513@gmail.com} $|$ 
  \href{https://www.linkedin.com/in/paul-jose-016}{linkedin.com/in/paul-jose-016} $|$ 
  \href{https://github.com/aeiou-sudo}{github.com/aeiou-sudo}
\end{center}

% Professional Summary
\section{Professional Summary}
Dedicated Front-End Developer with a strong background in computer science and a keen interest in developing efficient, scalable, and secure web applications. Proficient in HTML, CSS, JavaScript, and frameworks such as React and Bootstrap. Skilled at solving complex technical challenges and optimizing web performance.

% Technical Skills
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={\textbullet}]
    \item \textbf{Programming Languages:} Python, Java, C, Rust
    \item \textbf{Web Technologies:} JavaScript, HTML5, CSS, React, Bootstrap
    \item \textbf{Databases:} MySQL, SQLite

    \item \textbf{Tools:} Git, GitHub, IntelliJ IDEA, SSH (Secure Shell), Telnet, SIEM Tools, IDS, IPS
    \item \textbf{Cloud Services:} Google Cloud Platform (GCP)
    \item \textbf{Network Technologies:} IPv4, IPv6, OSPF, BGP, Spanning-tree, VLAN, WLAN, VPN
\end{itemize}

% Work Experience
\section{Work Experience}
\SectionTitle{Apprenticeship}
\textit{AT\&T Communications India Pvt. Ltd., Bengaluru} \hfill\textit {November 14, 2022 -- November 08, 2023}
\begin{itemize}[leftmargin=0.15in, label={\textbullet}]
  \item Apprenticeship focused on the Business Customer Experience BU, gaining hands-on training and exposure to advanced network technologies including IP, OSPF, BGP, VLAN, STP, and QoS.
  \item Supported Domain 1.0 customers in service activations and performed basic post-implementation troubleshooting for network deployments under the guidance of lead engineers.
  \item Demonstrated excellent performance, proactivity, and strong communication and interpersonal abilities, effectively collaborating with peers and external stakeholders.
\end{itemize}

% Projects
\section{Projects}
\makebox[\textwidth][s]{\SectionTitle{Facial Attendance Machine (Python)}\hfill\textit{Technologies: Python, Deep Neural Networks}}
\begin{itemize}[leftmargin=0.1in, label={\textbullet}]
  \item Designed and implemented a Python-based attendance monitoring system to replace our college's existing fingerprint biometric system, making it twice as fast and accurate.
  \item Utilized deep neural networks for facial recognition and attendance tracking, improving accuracy and speed compared to the existing system.
  \item Addressed usability issues faced by users with wet hands by providing a non-contact biometric solution.
\end{itemize}

\noindent\makebox[\textwidth][s]{\SectionTitle{Smart Farming Application (Java)}\hfill\textit{Technologies: Java, XML, Android Studio, SQLite}}
\begin{itemize}[leftmargin=0.1in, label={\textbullet}]
  \item Designed and launched an Android application during Covid-19 pandemic, enabling remote farm monitoring for individuals transitioning to farming.
  \item Addressed the challenge of monitoring farms remotely due to the distance between residences and farms, enhancing monitoring efficiency and security.
  \item Developed a real-time data monitoring and visualization feature in the app, incorporating a dynamic data table and video surveillance to deliver live updates and visual insights into farm conditions.
\end{itemize}

\noindent\makebox[\textwidth][s]{\SectionTitle{Portfolio Website (HTML, CSS)}\hfill\textit{Technologies: HTML, CSS}}
\begin{itemize}[leftmargin=0.1in, label={\textbullet}]
  \item Designed and developed a personal portfolio website to showcase projects and skills.
  \item Implemented a responsive design using CSS Grid and Flexbox, ensuring compatibility across devices.
\end{itemize}

% Education
\section{Education}
\textbf{Bachelor of Technology in Computer Science and Engineering (CSE)} \\
\textit{APJ Abdul Kalam Technological University, Kerala} \hfill\textit{August 2018 -- August 2022} 
\begin{itemize}[leftmargin=0.15in, label={\textbullet}]
  \item Graduated with a CGPA of 7.43/10
  \item Relevant Courses: Object Oriented Programming; Data Structures and Algorithms; Data Warehousing; Computer Networks; Cryptography; Data Science; Database Management Systems
\end{itemize}

% Certifications and Awards
\section{Certifications and Courses}

\SectionTitle{Responsive Web Design}
\textit{freeCodeCamp.org} \hfill\textit{August 2024} 

\SectionTitle{Google Cybersecurity Certificate}
\textit{Coursera - Grow With Google} \hfill\textit{March 2024} 

\SectionTitle{Python Full Stack Course}
\textit{Pentagon Space} \hfill\textit{May 2022} 

\SectionTitle{Introduction to Internet of Things}
\textit{NPTEL (Funded by the Ministry of HRD, Govt. of India)} \hfill\textit{October 2021} 

\SectionTitle{Architecting with Google Compute Engine}
\textit{Coursera} \hfill\textit{September 2021} 

% Additional Information
\section{Additional Information}
\begin{itemize}[leftmargin=0.15in, label={\textbullet}]
  \item \textbf{Languages:} Malayalam (Native), Tamil (Proficient), English (C1 IELTS)
  \item \textbf{Hobbies:} Reading technology blogs, hiking, traveling, volunteering, participating in coding challenges, learning new languages and cultures
  \item \textbf{Collaborative Teamwork:} Proven ability to work effectively with diverse teams to achieve project goals.
  \item \textbf{Analytical Thinking:} Skilled in identifying issues and developing strategic solutions.
  \item \textbf{Flexibility:} Quick to adapt to changing requirements and new technologies.
  \item \textbf{Effective Prioritization:} Proficient in managing time and tasks to meet deadlines.
\end{itemize}

\end{document}
